### 2013-03-30 doc/final_report/implementation.tex
Put in some stuff about JSON

Flask provides a model-view-controller style framework in which specific web
URLS are represented by `view' functions.

>>>>

Flask provides a model-view-controller style framework in which specific web
URLS are represented by `view' functions. The behaviour of these views changes
dependent upon data from the incoming HTTP request. Their return value is
encoded as an HTTP response and sent back to the browser that made the request.

The implementation of the server views was for the most part straight forward
with the exception of some of the responses to the interactive web elements in
the HTML markup. It was determined that the best way to communicate between
frontend and backend elements interactively was to encode responses as
JavaScript Object Notation JSON - a common notation used to describe arbitrary
data structures\cite{jsonRFC}. Despite its name, JSON encoders and decoders are available for
most common programming languages.  Flask even has an inbuilt method called
jsonify which can be used to automatically encode arbitrary Python objects as
JSON and send it back to the browser for parsing by the frontend scripts.
